\documentclass{article}[12pt]
\usepackage[a4paper, total={5.7in, 9in}]{geometry}

\begin{document}
\title{Title of your project}
\author{Your Name\\
{\em Your email address}}
\maketitle             

\section{Details of the proposal}
\label{sec:yourProposal}

Your proposal (full specification), the kind of your proposal (standard, creative), and the range on points associated with it (for standard projects) or the degree of difficulty (easy, medium, hard, for creative projects) should be made available here at the beginning of your report; this first page with information on you and on your proposal will not be counted in the number of pages of the report.

\subsection{Full specification of your proposal}
\label{subsec:specification}

\subsection{The kind of your proposal}
\label{subsec:kind}

\subsection{The range of points/difficulty of your proposal}
\label{subsec:points}

\pagebreak

\section{Introduction}
\label{sec:intro}

\subsection{One subsection of the Introduction}
\label{subsec:intro-level1}

\subsubsection{One subsubsection of the Introduction}
\label{subsubsec:intro-level2}

Use this style, with these margins, font dimension (12 pt) and space between lines, for the content of your report. 
\begin{itemize}
\item Projects which consist in a critical analysis and discussion of some topic related with the course must be at least 16 pages long, using this format. 
\item Projects which consist in experimenting existing tools must be at least 12 pages long. 
\item Projects which consist in the design/development of software must be accompanied by a document explaining the software itself, with basic instructions for its usage, and must be at least 8 pages long in this format.
    \end{itemize}
Whatever the type of the project, this report must be written in a good English: grammar and fluency errors will affect the final mark. 

\noindent Finally, note that plagiarism is a crime. If we will realize that you just copied and pasted pieces of information from the web, without any effort to understand and re-elaborate them, the assigned mark for the project will be 0 with no possibility to re-submit it. 

 \bibliographystyle{splncs04}
 \bibliography{bibliography}

\end{document}
